\bf Turkish Elections and Catastrophic Events

### 2021-12-11 paper/main.tex
Updates from Overleaf
new figures

\if0\blind
{
  \title{\bf Turkish Elections and Catastrophic Events}
    {
}

@@

The process of data cleaning and creation can be found in the author's \href{https://github.com/deniztokmakoglu/turkish_election_analysis}{github page.}

>>>>

\if0\blind
{
  \title{\bf Turkish Elections and Catastrophic Events}
    {
}
\author{\name Deniz Tokmakoglu\\
       \addr Harris Public Policy and Department of Computer Science\\
       \address{\href{https://github.com/deniztokmakoglu/turkish_election_analysis}{GitHub}}}
\maketitle

@@

Turkish election turnout is higher than most of the other democracies in the world. For all the election types and regions, the average turnout is $84\%$ Cities with the highest turnout appear to be on the east and south regions of Turkey, Istanbul being the exception.

\begin{figure}[h]
 \centering
\includegraphics[width=15cm]{paper/turnout_selected.png}
 \caption{Average Turnout for Selected Cities}
\end{figure}
\newpage
Cities in the South and East also appear to be shifting incumbent parties more than other cities, again Istanbul being an exception. While Eastern cities (Diyarbakır, Mardin and Van) always choose incumbent parties with same characteristics, cities like Adana always shift between Right and Left wing parties.

\begin{figure}[h]
 \centering
\includegraphics[width=15cm]{paper/change_party.png}
 \caption{Average Turnout for Selected Cities}
\end{figure}
